---
title: "Social Capital Analysis - Work in Progress"
output: html_document
---

# Background
This is an analysis project - work in progress - to calculate social capital values for each nation using available data. The first part of the project is to download suitable data from different sources, merge and prepare for data analysis.


# Download World Bank 
The World Bank 'Changing Wealth of nations dataset is available at http://data.worldbank.org/data-catalog/wealth-of-nations and has data for natural, produced and human capital for 120 countries.

```{r downloadWBdata,echo=FALSE,  warning=FALSE}
setwd("C:/Social Capital") #set a working directory for data - this directory needs to pre-exist
#Download file and put in working directory
#fileurl <- "http://data.worldbank.org/sites/default/files/total_and_per_capita_wealth_of_nations.xls"
#download.file(fileurl, 
#              destfile="./total_and_per_capita_wealth_of_nations.xls")

#convert file to dataframe
library(readxl)
readdata<-read_excel("total_and_per_capita_wealth_of_nations.xls",
                             sheet = "total wealth, 2005",na = c(".."))
WBdata_2005 <- data.frame(readdata[6:214,1:10])
colnames(WBdata_2005) <- readdata[5,1:10]
rownames(WBdata_2005) <- NULL
WBdata_2005[, c(5:10)] <- sapply(WBdata_2005[, c(5:10)], as.numeric)


```

A summary of the variables in this file, is below.


```{r viewdata,echo=FALSE}
str(WBdata_2005)
```


